### 2021-05-21 code/manuscript.Rmd
prepare all_fit

```{python, grand_averaging, eval=TRUE}
from os import makedirs

@@

  # Compute models for dependent variables in parallel
  dvs <- c("logRT", "P1", "N170", "N400")
  n_cores <- min(length(dvs), availableCores())
  plan("multisession", workers = n_cores)
  future_map(dvs, function(dv, dat = trials) {

@@

    # Fit initial model
    fit <- lmer(form, dat, REML = FALSE)

@@

    # See which of the optimizers converged
    fits_converged <- keep(
      fits,
      ~ .x@optinfo$conv$opt == 0 &
        length(.x@optinfo$conv$lme4) == 0 &
        length(.x@optinfo$warnings) == 0
    )

@@

```{r, fig3, include=TRUE}
evo_tfr_flat <- read_csv(fnames$evo_tfr_flat, col_types = cols(), progress = FALSE)
evo_tfr_diff <- read_csv(fnames$evo_tfr_diff, col_types = cols(), progress = FALSE)

@@

# Time-frequency of interest based on visual inspect
tfoi <- list(tmin = 200, tmax = 400, fmin = 34, fmax = 48)  # Gamma
# tfoi <- list(tmin = 150, tmax = 350, fmin = 14, fmax = 24)  # Beta

standard_text <- element_text(size = 10, color = "black", family = "Helvetica")

>>>>

```{python, grand_averaging, eval=rerun_preprocessing}
from os import makedirs

@@

  # Compute models for dependent variables in parallel
  dvs <- c("logRT", "P1", "N170", "N400")
  n_cores <- min(length(dvs), availableCores())
  plan("multicore", workers = n_cores)
  future_map(dvs, function(dv, dat = trials) {

@@

    # Fit initial model
    fit <- lmer(form, dat, REML = TRUE)

@@

    # See which of the optimizers converged
    fits_converged <- keep(
      fits,
      ~ .x@optinfo$conv$opt == 0 & length(.x@optinfo$conv$lme4) == 0
    )

@@

```{r, fig3, include=TRUE}
# Read grand averages of evoked power
evo_tfr_flat <- read_csv(fnames$evo_tfr_flat, col_types = cols(), progress = FALSE)
evo_tfr_diff <- read_csv(fnames$evo_tfr_diff, col_types = cols(), progress = FALSE)

@@

# Time-frequency of interest based on visual inspect
tfoi <- list(tmin = 150, tmax = 350, fmin = 14, fmax = 24)  # Beta or
tfoi <- list(tmin = 200, tmax = 400, fmin = 34, fmax = 48)  # Gamma

# Standard text format
standard_text <- element_text(size = 10, color = "black", family = "Helvetica")
